---
title: "flat_teaching.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{=html}
<!-- 
Run this 'development' chunk

Store every call to library() that you need to run chunks line by line, as in a classical Rmd for analysis
-->
```
```{r development, include=FALSE}
library(data.table)
library(ggplot2)
library(tidyfst)
library(robustbase)
library(taskscheduleR)
library(patchwork)
library(lubridate)
```

```{=html}
<!--
# Description of your package

This will fill the description of your package.
Fill and run the content of this chunk, before anything else. 

Note: when you will use other flat templates, this part will be in a separate file. Do not be surprised!
-->
```
```{r description, eval=FALSE}
# Describe your package
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "Breeding Tools",
    Description = "An R package that can monitor the csv data and stations from the Nedap in pig farm.",
     `Authors@R` = c(
      person("Guo Meng", email = "tony2015116@163.com", role = c("aut", "cre")),
      person(given = "Guo Meng", role = "cph")
    )
  ),
  overwrite=T
)
# Define License with use_*_license()
usethis::use_mit_license("Guo Meng")
```

# Feed intake monitor of pigs

This is the first tool of our wonderful package. You can add `1` to any `value` using function `fid_monitor()`.

```{r function-fid_monitor}
#' Feed intake monitor of pig performance test station
#' 
#' @param data Csv data of pig performance test station
#' @param station_type Type of pig performance test station, you can choose nedap or fire
#' @param save_path A string specifying the output file path
#' 
#' @importFrom data.table ":="
#' @importFrom data.table ".SD"
#' 
#' @return A pdf file about feed intake data monitor
#' @export
#' 
fid_monitor <- function(data, station_type, save_path) {
  if (missing(data)) stop("Please provide 'data' argument.")
  if (missing(station_type)) stop("Please provide 'station_type' argument.")
  if (missing(save_path)) stop("Please provide 'save_path' argument.")
  # Argument checks
  if (!is.data.frame(data) && !data.table::is.data.table(data)) {
    stop("The 'data' argument must be a data.frame or a data.table.")
  }

  if (!is.character(station_type) || !(station_type %in% c("nedap", "fire"))) {
    stop("The 'station_type' argument must be either 'nedap' or 'fire'.")
  }

  if (!is.character(save_path) || !dir.exists(save_path)) {
    stop("The 'save_path' argument must be a valid directory path.")
  }
  visit_time <- . <- location <- responder <- feed_intake <- all_feed_a_station_one_day <- total_intake <- percent_intake <- Date <- Consumed <- total_intake <- percent_intake <- ndt <- plot1 <- plot2 <- NULL

  if (!data.table::is.data.table(data)) {
    data <- data.table::setDT(data)
  }
  prepare_nedap_data <- function(data) {
    temp1 <- unique(data)[,`:=`(c("date", "time"),data.table::tstrsplit(visit_time," ", fixed = TRUE))][, `:=`(c("date"), lubridate::ymd(date))][,!c("visit_time", "time")]
    temp2 <- temp1[, keyby = .(location, responder, date),.(total_intake = round(sum(feed_intake) / 1000, digits = 4))][,`:=`(all_feed_a_station_one_day, sum(total_intake)), by = .(location, date)][, `:=`(percent_intake, total_intake / all_feed_a_station_one_day)]
    to_factor = c("location", "responder")
    temp2[, `:=`((to_factor), purrr::map(.SD, as.factor)), .SDcols = to_factor]
    return(temp2)
  }

  prepare_fire_data <- function(data) {
    temp1 <- unique(data)[,`:=`(Date, lubridate::ymd(Date))]
    data.table::setnames(temp1, 1:3, c("location", "responder","date"))
    temp2 <- temp1[, keyby = .(location, responder, date),.(total_intake = round(sum(Consumed), digits = 4))][,`:=`(all_feed_a_station_one_day, sum(total_intake)),by = .(location, date)][, `:=`(percent_intake, total_intake / all_feed_a_station_one_day)]
    to_factor = c("location", "responder")
    temp2[, `:=`((to_factor), purrr::map(.SD, as.factor)),.SDcols = to_factor]
    return(temp2)
  }

  # Prepare data based on station_type
  if (station_type == "nedap") {
    prepared_data <- prepare_nedap_data(data)
  } else if (station_type == "fire") {
    prepared_data <- prepare_fire_data(data)
  } else {
    stop("Invalid station_type. Supported types are 'nedap' and 'fire'.")
  }

  # Create the plots
  colors = c("#a6cee3", "#1f78b4", "#b2df8a", "#33a02c", "#fb9a99", "#e31a1c", "#fdbf6f", "#ff7f00", "#cab2d6", "#6a3d9a", "#b15928", "#8dd3c7", "#d9d9d9", "#80b1d3", "#00AFBB", "#01665e", "#003c30", "blue", "pink", "yellow", "red", "green", "#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#00AFBB", "#E7B800", "#FC4E07", "#1B9E77", "#D95F02", "#7570B3", "#E7298A", "#66A61E", "#E6AB02", "#A6761D", "#666666", "purple")
  #colors = as.character(palette.colors(n = 36, "Polychrome 36"))

  create_plots <- function(data, ...) {
    data[, list(list(.SD)), by = location
    ][, `:=`("plot1", purrr::map2(.SD[[1]], location, ~ ggplot2::ggplot(
      data = .x,
      ggplot2::aes(y = percent_intake,
                   x = date, fill = responder)
    ) + ggplot2::theme_bw() +
      ggplot2::geom_col(
        width = 0.8,
        na.rm = F,
        show.legend = T
      ) +
      ggplot2::ggtitle(.y) + ggplot2::scale_y_continuous(
        labels = scales::percent,
        limits = c(0, 1),
        breaks = seq(0, 1, 0.1)
      ) + ggplot2::theme(
        plot.title = ggplot2::element_text(
          color = "black",
          hjust = 0.5,
          size = 20
        ),
        axis.title.x = ggplot2::element_blank(),
        axis.title.y = ggplot2::element_text(size = 15),
        axis.text.x = ggplot2::element_text(size = 8, angle = 270),
        axis.text.y = ggplot2::element_text(size = 8),
        legend.title = ggplot2::element_text(size = 8),
        legend.text = ggplot2::element_text(size = 8),
        legend.position = "top"
      ) +
      ggplot2::guides(
        shape = ggplot2::guide_legend(override.aes = list(size = 7)),
        color = ggplot2::guide_legend(override.aes = list(size = 7))
      ) +
      ggplot2::ggtitle(paste0("location:", .y)) + ggplot2::scale_x_date(
        date_breaks = "1 day",
        date_labels = "%m-%d",
        date_minor_breaks = "1 day"
      ) +
      ggplot2::scale_fill_manual(
        na.value = "black",
        values = colors
      ), ...)), .SDcols = "V1"
    ][, `:=`("plot2", purrr::map2(.SD[[1]], location, ~ ggplot2::ggplot(data = .x,
                                                                        ggplot2::aes(
                                                                          y = total_intake, x = date, fill = responder
                                                                        )) +
                                    ggplot2::theme_bw() + ggplot2::geom_col(
                                      width = 0.8,
                                      na.rm = F,
                                      show.legend = F
                                    ) + ggplot2::theme(
                                      plot.title = ggplot2::element_text(
                                        color = "black",
                                        hjust = 0.5,
                                        size = 20
                                      ),
                                      axis.title.x = ggplot2::element_text(size = 15),
                                      axis.title.y = ggplot2::element_text(size = 15),
                                      axis.text.x = ggplot2::element_text(size = 8, angle = 270),
                                      axis.text.y = ggplot2::element_text(size = 8),
                                      legend.position = "none"
                                    ) +
                                    ggplot2::guides(
                                      shape = ggplot2::guide_legend(override.aes = list(size = 7)),
                                      color = ggplot2::guide_legend(override.aes = list(size = 7))
                                    ) +
                                    ggplot2::scale_x_date(
                                      date_breaks = "1 day",
                                      date_labels = "%m-%d",
                                      date_minor_breaks = "1 day"
                                    ) + ggplot2::scale_fill_manual(
                                      na.value = "black",
                                      values = colors
                                    ), ...)), .SDcols = "V1"][]
  }

  # Combine and save the plots
  save_combined_plots <- function(path_out) {
    temp_plot <- create_plots(data = prepared_data, value = colors)

    # Calculate the number of unique locations
    num_locations <- length(unique(temp_plot$location))

    # Calculate the date range
    date_range <- range(prepared_data$date)
    num_days <- as.numeric(difftime(date_range[2], date_range[1], units = "days")) + 1

    # Calculate the PDF dimensions based on the number of locations and date range
    width_per_day <- 0.3 # 0.5 cm per day, you can adjust this value based on your preferences
    pdf_width <- num_days * width_per_day * 2 # Adjust width according to the date range and number of columns

    height_per_location <- 30 # 5 cm per location, you can adjust this value based on your preferences
    pdf_height <- height_per_location * ceiling(num_locations / 2) # Adjust height according to the number of locations and number of rows


    temp4 <- temp_plot[, `:=`("finals", purrr::pmap(.(.SD[[1]], .SD[[2]]), function(x, y) patchwork::wrap_plots(x, y, ncol = 1))), .SDcols = c("plot1","plot2")][]
    temp5 <- patchwork::wrap_plots(temp4$finals, ncol = 2)


    ggplot2::ggsave(
      file.path(save_path, "feed_intake_monitor.pdf"),
      temp5,
      width = pdf_width,
      height = pdf_height,
      units = "cm",
      dpi = "retina",
      limitsize = FALSE
    )
  }
  save_combined_plots(save_path)
}
```

```{r examples-stations_monitor}
data <- data.table::fread("C:/Users/Dell/Downloads/test/ppt_test_data.csv")
fid_monitor(data = data, station_type = "nedap", save_path = "C:/Users/Dell/Downloads/test")
```

```{=html}
<!-- 
This first section shows:

- the three parts necessary for a package: 'function', 'examples' and 'tests'.  
  + Note that the three following chunks have names accordingly.

-->
```
```{=html}
<!--
Here is an example on how to use the function.
This should be a reproducible and working example
-->
```
# station_monitor

```{r function-station_monitor}
#' Feed intake monitor of pig performance test station
#' 
#' @param data Csv data of pig performance test station
#' @param station_type Type of pig performance test station, you can choose nedap or fire
#' @param save_path A string specifying the output file path
#' 
#' @importFrom data.table ":=" "CJ" ".SD"
#' 
#' @return png files about stations monitor
#' @export
#' 
station_monitor <- function (data, station_type, save_path)
{
  if (missing(data)) stop("Please provide 'data' argument.")
  if (missing(station_type)) stop("Please provide 'station_type' argument.")
  if (missing(save_path)) stop("Please provide 'save_path' argument.")
  # Argument checks
  if (!is.data.frame(data) && !data.table::is.data.table(data)) {
    stop("The 'data' argument must be a data.frame or a data.table.")
  }

  if (!is.character(station_type) || !(station_type %in% c("nedap", "fire"))) {
    stop("The 'station_type' argument must be either 'nedap' or 'fire'.")
  }

  if (!is.character(save_path) || !dir.exists(save_path)) {
    stop("The 'save_path' argument must be a valid directory path.")
  }
  visit_time <-
    responder <-
    . <-
    location <-
    animal_number <-
    duration <-
    feed_intake <-
    Entry <-
    Exit <- Consumed <- weight <- ndt <- . <- items <- plot1 <- .N <- V1 <- hour <- plot_name <- NULL

  if (!data.table::is.data.table(data)) {
    data <- data.table::setDT(data)
  }
  # Prepare data based on station_type
  prepare_nedap_data <- function(data) {
    temp1 <-
      unique(data)[, `:=`(c("date", "time"),data.table::tstrsplit(visit_time," ", fixed = TRUE))
                   ][, `:=`(c("date"), data.table::as.IDate(date))
                     ][,!c("visit_time", "time")]
    temp2 <- unique(temp1, by = c("location", "responder", "date"))[!is.na(responder)
                                                                    ][, keyby = .(location,date), .(animal_number = .N)]
    temp3 <- temp1[!is.na(animal_number)
                   ][, keyby = .(location,date), .(`total_intake_duration(min)` = round(sum(duration) / 60,digits = 4),total_intake = round(sum(feed_intake) / 1000,digits = 4),visit_number = .N)]
    temp5 <- merge(temp2, temp3, all.x = TRUE)
    list(temp5 = temp5, temp1 = temp1)
  }

  prepare_fire_data <- function(data) {
    temp1 <- unique(data)[, `:=`(Entry,do.call(paste, c(.SD, sep = " "))), .SDcol = c("Date","Entry")
                          ][, `:=`(Exit, do.call(paste, c(.SD, sep = " "))),.SDcol = c("Date", "Exit")
                            ][, `:=`(c("Entry", "Exit"),lapply(.SD, lubridate::ymd_hms)), .SDcol = c("Entry","Exit")
                              ][, `:=`(duration,data.table::fifelse(Exit -Entry < 0 & lubridate::hour(Exit) == 0,Exit - Entry + lubridate::ddays(1), Exit - Entry))]
    data.table::setnames(temp1,
                         c(1:3, 9),
                         c("location",
                           "responder", "date", "weight"))
    temp1 <- unique(temp1)[, `:=`(date, lubridate::ymd(date))]
    temp2 <- unique(temp1, by = c("location", "responder","date"))[!is.na(responder)
                                                                   ][, keyby = .(location, date), .(animal_number = .N)]
    temp3 <- temp1[!is.na(responder)
                   ][, `:=`(duration, as.numeric(duration))
                     ][,keyby = .(location, date), .(`total_intake_duration(min)` = round(sum(duration) / 60,digits = 4), total_intake = round(sum(Consumed),digits = 4),visit_number = .N)]
    temp5 <- merge(temp2, temp3, all.x = TRUE)
    list(temp5 = temp5, temp1 = temp1)
  }


  # Prepare data based on station_type
  if (station_type == "nedap") {
    prepared_data_list <- prepare_nedap_data(data)
    prepared_data <- prepared_data_list$temp5
    temp1 <- prepared_data_list$temp1
  } else if (station_type == "fire") {
    prepared_data_list <- prepare_fire_data(data)
    prepared_data <- prepared_data_list$temp5
    temp1 <- prepared_data_list$temp1
  } else {
    stop("Invalid station_type. Supported types are 'nedap' and 'fire'.")
  }

  # The rest of the code remains the same.
  # 将第3到第6列的类型转换为numeric
  prepared_data[, (3:6) := lapply(.SD, as.numeric), .SDcols = 3:6]

  # 使用melt函数
  temp6 = data.table::melt(prepared_data,
                           id.vars = c("location", "date"),
                           measure.vars = 3:6,
                           variable.name = "items",
                           value.name = "values")

  temp6_2 <- temp1[!is.na(location), .(location, date, weight)
  ][, list(list(.SD)), by = location # nest by location
  ][, `:=`("V1", purrr::map(.SD[[1]], function(data) {data[data.table::CJ(date = tidyr::full_seq(date, 1)), on = .(date)
  ][data.table::CJ(date = date, unique = TRUE), on = .(date)]})), .SDcols = "V1"
  ][, `:=`("plot1", purrr::map2(.SD[[1]], location, ~ggplot2::ggplot(data = .x, ggplot2::aes(x = date, y = weight, group = date)) +
                                  ggplot2::geom_boxplot(outlier.color = "red") +
                                  cowplot::background_grid(minor = "none") +
                                  ggplot2::scale_x_date(date_breaks = "1 day", date_labels = "%d") +
                                  ggplot2::theme_bw() +
                                  ggplot2::theme(legend.position = "none",
                                                 axis.title.x = ggplot2::element_blank(),
                                                 axis.text.x = ggplot2::element_text(angle = -90),
                                                 axis.text = ggplot2::element_text(size = 8)))), .SDcols = "V1"
    ][ , V1 := NULL
       ][]

  temp7 <- temp6[, list(list(.SD)), by = location
  ][, `:=`("V1", purrr::map(.SD[[1]], function(data) {data[CJ(date = tidyr::full_seq(date, 1)), on = .(date)
  ][CJ(date = date, items = items, unique = TRUE), on = .(date, items)
  ][!is.na(items)
  ][,`:=`(items, factor(items, labels = c("N", "visit_time/min","feed_intake/kg", "visit_number")))]})), .SDcols = "V1"
  ][, `:=`("plot2", purrr::map2(.SD[[1]], location,~ggplot2::ggplot(data = .x, ggplot2::aes(x = date, y = values)) +
                                  ggplot2::geom_point(ggplot2::aes(col = items)) +
                                  ggplot2::geom_line(ggplot2::aes(col = items)) +
                                  ggplot2::theme_bw() +
                                  ggplot2::facet_grid(items ~ ., scales = "free") +
                                  ggplot2::scale_x_date(date_breaks = "1 day", date_labels = "%m") +
                                  ggplot2::scale_colour_brewer(palette = "Set1") +
                                  ggplot2::theme(strip.text.y = ggplot2::element_text(angle = 0,hjust = 0),
                                                 legend.position = "none",
                                                 axis.title = ggplot2::element_blank(),
                                                 axis.text.x = ggplot2::element_text(angle = -90),
                                                 axis.text = ggplot2::element_text(size = 8),
                                                 strip.placement = "outside",
                                                 strip.background = ggplot2::element_rect(colour = "white", fill = "white")) +
                                  ggplot2::ggtitle(paste0("Location:", .y)) +
                                  cowplot::background_grid(minor = "none"))), .SDcols = "V1"][]

  temp8 <- merge(temp7, temp6_2, by = "location", all.x = TRUE)
  temp9 <- temp8[, `:=`("finals", purrr::pmap(.(.SD[[1]], .SD[[2]]), function(x, y) patchwork::wrap_plots(x, y, nrow = 2))), .SDcols = c("plot2","plot1")
  ][, plot_name := paste0(location, "_stations.png")][]

  # 根据天数计算图片的长度和宽度
  # 使用 map() 遍历 V1 列中的所有列表，计算唯一日期数
  days <- purrr::map_dbl(temp9$V1, ~ length(unique(.x$date)))
  height <- ifelse(days <= 7, 6, ifelse(days <= 14, 6, ifelse(days <= 30, 6, 6)))
  width <- ifelse(days <= 7, 3, ifelse(days <= 14, 8, ifelse(days <= 30, 13, 16)))

  purrr::walk2(
    temp9$plot_name,
    temp9$finals,
    ~ ggplot2::ggsave(
      filename = file.path(save_path, .x),
      plot = .y,
      height = height,
      width = width
    )
  )
}
```

```{r examples-station_monitor}
data <- data.table::fread("C:/Users/Dell/Downloads/test/ppt_test_data.csv")
station_monitor(data = data, station_type = "nedap", save_path = "C:/Users/Dell/Downloads/test")
```

This is the first tool of our wonderful package. You can add `1` to any `value` using function `station_monitor()`.

# growth_monitor

This is the first tool of our wonderful package. You can add `1` to any `value` using function `growth_monitor()`.

```{r function-growth_monitor}
#' Feed intake monitor of pig performance test station
#' 
#' @param data Csv data of pig performance test station
#' @param lmrob Default lmrob = TRUE
#' @param threshold Defult threshold is 0.8
#' @param my_break Default break is NULL
#' @param range_offset Default range_offset is 0.5
#' @param save_path A string specifying the output file path
#' 
#' @importFrom data.table ":=" ".SD"
#' @importFrom stats "coef" "predict" "residuals" "sd"
#' 
#' @return png files about growth curve monitor in each station
#' @export
#' 
growth_monitor <- function(data, lmrob = T, threshold = 0.8, my_break = NULL, range_offset = 0.5, save_path) {
  # Argument check
  if (missing(data)) stop("Please provide 'data' argument.")
  if (missing(save_path)) stop("Please provide 'save_path' argument.")
  if (!(is.data.frame(data) || data.table::is.data.table(data))) stop("data must be a data.frame or data.table")
  if (!is.character(save_path)) stop("save_path must be a character string")
  if (!is.logical(lmrob)) stop("lmrob must be a logical value.")
  if (!is.numeric(threshold) || length(threshold) != 1) stop("threshold must be a numeric value.")

  if (lmrob) {if (threshold < 0.5 || threshold > 1.5) {stop("When lmrob is TRUE, threshold should be between 0.5 and 1.5.")}} else {
    if (threshold < 0.5 || threshold > 0.99) {stop("When lmrob is FALSE, threshold should be between 0.5 and 0.99.")}}

  if (!is.null(my_break) && (!is.numeric(my_break) || length(my_break) != 2)) stop("my_break must be either NULL or a numeric vector with two elements.")

  if (!is.numeric(range_offset) || length(range_offset) != 1) stop("range_offset must be a numeric value.")

  #if (range_offset < 0.5 || range_offset > 1) stop("range_offset should be between 0.5 and 1.")

  . <- .GRP <- .N <- color_judge <- day_diff <- day_text <- error_msg <- lm_predict <- lm_slope <- location <- mean_residual <- model_lmrob <- model_rlm <- n_days <- n_responders <- outliers <- r_squared <- responder <- safe_lm <- safe_lmrob <- safe_rlm <- sd_residual <- seq_days <- seq_in_day <- stage <- visit_time <- w <- warning_msg <- weight <- NULL

  # The rest of your function
  # function of data process
  process_data <- function(data) {
    if (is.data.frame(data)) data <- data.table::as.data.table(data)

    data <- unique(data)[!is.na(responder)
    ][, `:=`(c("date", "time"), data.table::tstrsplit(visit_time, " ", fixed = TRUE))
    ][, `:=`(date, lubridate::ymd(as.Date(date)))
    ][order(visit_time), `:=`(seq_days, .GRP), by = date
    ][order(visit_time), `:=`(seq_in_day, 1:.N), by = .(responder, date)
    ][order(responder, visit_time)
    ][, c("responder", "location", "date", "seq_days", "seq_in_day", "weight")
    ][, .(data = list(.SD)), responder][]

    return(data)
  }

  # Check for errors and warnings and print messages
  check_errors_and_warnings <- function(data) {
    # Check for errors
    if (any(data[, error_msg != ""])) {
      cat("Errors encountered during processing:\n")
      cat(data[data[, error_msg != ""], .(responder, error_msg)], sep = "\n")
    } else {
      cat("No errors encountered during processing.\n")
    }

    # Check for warnings
    if (any(data[, warning_msg != ""])) {
      cat("Warnings encountered during processing:\n")
      cat(data[data[, warning_msg != ""], .(responder, warning_msg)], sep = "\n")
    } else {
      cat("No warnings encountered during processing.\n")
    }
  }

  # 使用RANSAC进行鲁棒线性回归
  process_lmrob_results <- function(data, threshold, ...) {
    safelmrob <- purrr::safely(.f = robustbase::lmrob)
    temp1 <- data[, `:=`(safe_lmrob, purrr::map(data, function(df, ...) safelmrob(..., data = df), ...))
    ][, `:=`(model_lmrob, purrr::map(safe_lmrob, function(x) x$result))
    ][, `:=`(error_msg, purrr::map_chr(safe_lmrob, function(x) if (is.null(x$error)) "" else x$error$message))
    ][, `:=`(warning_msg, purrr::map_chr(safe_lmrob, function(x) if (is.null(x$warning)) "" else x$warning$message))
    ][, `:=`(residuals, purrr::pmap(list(model_lmrob, error_msg, warning_msg), function(x, e, w) {
      if (e == "" && w == "") {return(residuals(x))} else {return(NULL)}}))
    ][, `:=`(predict, purrr::pmap(list(model_lmrob, error_msg, warning_msg), function(x, e, w) {
      if (e == "" && w == "") {return(predict(x))} else {return(NULL)}}))
    ][, `:=`(mean_residual, purrr::map_dbl(residuals, mean, na.rm = TRUE))
    ][, `:=`(sd_residual, purrr::map_dbl(residuals, sd, na.rm = TRUE))
    ][, `:=`(outliers, purrr::pmap(list(residuals, mean_residual, sd_residual), function(r, m, sd) {
      if (length(r) > 0) {return(abs(r - m) > threshold * sd)} else {return(NULL)}}))
    ][]#
    check_errors_and_warnings(temp1)
    temp2 = temp1[, c("safe_lmrob","model_lmrob","error_msg","warning_msg","residuals","mean_residual","sd_residual") := NULL
    ][, tidyfst::unchop_dt(.SD), .SDcol = c("data", "predict", "outliers"), by = responder]
    return(temp2)
  }

  # Fit rlm models for each data subset
  process_rlm_results <- function(data, threshold, ...) {
    saferlm <- purrr::safely(.f = MASS::rlm)
    temp1 <- data[, `:=`(safe_rlm, purrr::map(data, function(df, ...) saferlm(..., data = df), ...))
    ][, `:=`(model_rlm, purrr::map(safe_rlm, function(x) x$result))
    ][, `:=`(error_msg, purrr::map_chr(safe_rlm, function(x) if (is.null(x$error)) "" else x$error$message))
    ][, `:=`(warning_msg, purrr::map_chr(safe_rlm, function(x) if (is.null(x$warning)) "" else x$warning$message))
    ][, `:=`(predict, purrr::pmap(list(model_rlm, error_msg, warning_msg), function(x, e, w) {
      if (e == "" && w == "") {return(predict(x))} else {return(NULL)}}))
    ][][, `:=`(w, purrr::map(model_rlm, function(x) if (!is.null(x)) x$w else NA))
    ][, `:=`(outliers, purrr::map(w, function(x) if (!is.null(x)) x < threshold else NA))
    ][]
    check_errors_and_warnings(temp1)
    temp2 = temp1[, c("safe_rlm","model_rlm","error_msg","warning_msg") := NULL
    ][, tidyfst::unchop_dt(.SD), .SDcol = c("data", "predict", "outliers"), by = responder]
    return(temp2)

    return(temp2)
  }

  #一般线性模型计算日增重
  process_lm_results <- function(data, ...) {
    safelm = purrr::safely(.f = stats::lm)
    temp1 <- data[outliers == FALSE]
    temp2 <- temp1[, .(data = list(.SD)), by = responder
    ][, `:=`(safe_lm, purrr::map(data, function(df, ...) safelm(..., data = df), ...))
    ][, `:=`(safe_lm, purrr::map(safe_lm, function(x) x$result))
    ][, `:=`(error_msg, purrr::map_chr(safe_lm, function(x) if (is.null(x$error)) "" else x$error$message))
    ][, `:=`(warning_msg, purrr::map_chr(safe_lm, function(x) if (is.null(x$warning)) "" else x$warning$message))
    ][, `:=`(lm_predict, purrr::map2(safe_lm, warning_msg, function(x, w) if (w == "") stats::predict(x) else NA))
    ][, `:=`(lm_slope, purrr::map(safe_lm, function(x) coef(x)["seq_days"]))
    ][, `:=`(r_squared, purrr::map_dbl(safe_lm, function(x) if (!is.null(x)) summary(x)$r.squared else NA))]
    check_errors_and_warnings(temp2)
    temp3 <- temp2[, c("responder", "lm_slope", "r_squared")][]
    final <- temp3 |> tidyfst::unnest_dt(lm_slope)
    return(final)
  }

  # Create plots
  create_plots <- function(data) {
    data <- data[, `:=`(color_judge, data.table::fifelse(outliers == F, "Normal", "Outlier"))
    ][, .(data = list(.SD)), location]

    data[, `:=`(plot, purrr::map2(data, location, function(.x, .y) {
      slopes_and_r_squared <- .x[, .(lm_slope = unique(lm_slope), r_squared = unique(r_squared)), by = responder]

      if (!is.null(my_break)) {
        slopes_and_r_squared[, day_diff := (my_break[2] * 1000 - my_break[1] * 1000) / lm_slope]
        slopes_and_r_squared[, day_text := sprintf("Slope: %.2f, R^2: %.2f\n%d~%d kg: %.1f days", lm_slope, r_squared, my_break[1], my_break[2], day_diff)]
      } else {
        slopes_and_r_squared[, day_text := sprintf("Slope: %.2f, R^2: %.2f", lm_slope, r_squared)]
      }

      ggplot2::ggplot(data = .x, ggplot2::aes(x = date, y = weight)) +
        ggplot2::theme_bw() +
        ggplot2::geom_point(ggplot2::aes(col = color_judge), size = 1, na.rm = T) +
        ggplot2::scale_color_manual(values = c(Normal = "#38b48b", Outlier = "#b81a35"), name = "robust regression") +
        ggplot2::scale_x_date(date_breaks = "1 day", date_labels = "%m-%d") +
        ggplot2::geom_line(ggplot2::aes(x = date, y = predict), na.rm = T) +
        ggplot2::facet_wrap( ~ as.numeric(responder), ncol = 2) +
        ggplot2::scale_y_continuous(breaks = seq(15000, 130000, 10000), limits = c(15000, 130000)) +
        ggplot2::labs(title = paste("Location:", .y)) +
        ggplot2::theme(legend.position = "bottom",
                       legend.title = ggplot2::element_text(size = 20),
                       legend.text = ggplot2::element_text(size = 20),
                       axis.text.x = ggplot2::element_text(angle = -90, size = 10),
                       plot.title = ggplot2::element_text(size = 25, face = "bold")
        ) +
        ggplot2::geom_hline(yintercept = 30000, linetype = "dashed", color = "#aed0ee") +
        ggplot2::geom_hline(yintercept = 60000, linetype = "dashed", color = "#aed0ee") +
        ggplot2::geom_hline(yintercept = 115000, linetype = "dashed", color = "#aed0ee") +
        ggplot2::geom_text(data = slopes_and_r_squared, mapping = ggplot2::aes(label = day_text, x = min(.x$date), y = 130000, group = responder), hjust = 0, vjust = 1, size = 3)
    }))]
    return(data)
  }

  #看情况，最好是过滤掉异常体重数据后再截取体重
  cut_weight <- function(data, my_break, range_offset) {
    if (is.data.frame(data)) data <- data.table::as.data.table(data)

    # 将my_break乘以1000以匹配数据中的体重表示
    my_break <- my_break * 1000

    # 使用给定的范围和范围偏移生成实际的断点
    actual_breaks <- c(my_break[1] - range_offset * 1000, my_break[2] + range_offset * 1000)

    # 选取指定范围内的体重
    data <- data[predict >= actual_breaks[1] & predict <= actual_breaks[2], ]

    # 添加stage列，用于表示选取的体重范围
    data[, `:=`(stage, paste0(my_break[1] / 1000, "-", my_break[2] / 1000))]

    return(data)
  }

  #保存图片
  save_plots <- function(data, save_path) {
    # 计算每个location中的responder数量和date天数
    location_dims <- data[, .(n_responders = data.table::uniqueN(data[[1]]$responder),
                              n_days = data.table::uniqueN(data[[1]]$date)), by = location]

    # 调整图像的宽度和高度
    adjusted_dims <- location_dims[, .(width = 0.7 * n_days, height = 6 * n_responders)]

    # 保存图像
    purrr::walk2(file.path(save_path, paste0("location_", data$location, "_growth.png")), data$plot,
                 function(file, plot, width, height) {
                   ggplot2::ggsave(filename = file, plot = plot, width = width, height = height, units = "cm", dpi = "retina")
                 }, width = adjusted_dims$width, height = adjusted_dims$height)
  }

  # 函数调用
  processed_data <- process_data(data)

  if (lmrob) {
    # 设置RANSAC参数
    control <- robustbase::lmrob.control(tuning.chi = 1.548, k.max = 1000, maxit.scale = 1000, max.it = 1000)
    lm_results <- process_lmrob_results(data = processed_data, threshold = threshold, weight ~ seq_days, control= control)
  } else {
    lm_results <- process_rlm_results(data = processed_data, threshold = threshold, weight ~ seq_days + I(seq_days^2), maxit=5000)
  }

  slopes <- process_lm_results(data = lm_results, weight ~ seq_days)

  if (!is.null(my_break)) {
    cut_data <- cut_weight(data = lm_results, my_break = my_break, range_offset = range_offset)
    slopes_cut <- process_lm_results(data = cut_data, weight ~ seq_days)
    final_cut <- merge(cut_data, slopes_cut, by = "responder")
    plots_cut <- create_plots(final_cut)
    save_plots(plots_cut, save_path)
  } else {
    final <- merge(lm_results, slopes, by = "responder")
    plots <- create_plots(final)
    save_plots(plots, save_path)
  }
}
```

```{r examples-growth_monitor}
data <- data.table::fread("C:/Users/Dell/Downloads/test/ppt_test_data.csv")
growth_monitor(data = data, save_path = "C:/Users/Dell/Downloads/test")
```

# monitor_schedule

```{r function-monitor_schedule}
#' Feed intake monitor of pig performance test station
#' 
#' @description
#'
#' `monitor_schedule()` is deprecated. We will soon be totally
#' 
#' @param taskname A character string with the name of the task. Defaults to the filename. Should not contain any spaces
#' @param schedule Either one of 'ONCE', 'MONTHLY', 'WEEKLY', 'DAILY', 'HOURLY', 'MINUTE', 'ONLOGON', 'ONIDLE
#' @param starttime A timepoint in HH:mm format indicating when to run the script. Defaults to within 62 seconds
#' @param startdate A date that specifies the first date on which to run the task. Only applicable if schedule is of type 'MONTHLY', 'WEEKLY', 'DAILY', 'HOURLY', 'MINUTE'. Defaults to today in '%d/%m/%Y' format. Change to your locale format if needed
#' @param rscript_args Character string with further arguments passed on to Rscript
#' @param ... other parameters
#'
#' @importFrom utils "capture.output"
#'
#' @return CSV files in the path of save_path
#' @export
#' 
monitor_schedule <- function(taskname, schedule, starttime, startdate, rscript_args = NULL, ...) {
  if (missing(taskname) || !is.character(taskname) || length(taskname) != 1) {
    stop("taskname must be a single character string")
  }
  
  if (missing(schedule) || !is.character(schedule) || length(schedule) != 1) {
    stop("schedule must be a single character string")
  }
  
  if (missing(starttime) || !is.character(starttime) || length(starttime) != 1) {
    stop("starttime must be a single character string")
  }
  
  if (missing(startdate) || !is.character(startdate) || length(startdate) != 1) {
    stop("startdate must be a single character string")
  }
  
  if (missing(rscript_args) || !is.list(rscript_args)) {
    stop("rscript_args must be a list of arguments")
  }
  
  # Save the function to a temporary script file with a shorter path
  short_temp_path <- "C:/Temp"
  dir.create(short_temp_path, showWarnings = FALSE)
  script_file <- file.path(short_temp_path, paste0(taskname, "_", sample(letters, 1), ".R"))
  
  my_function <- function(csv_path, ...) {
    csv_files <- list.files(csv_path, full.names = T, pattern = ".csv")
    csv_data <- pptos::import_csv(csv_files, package = "data.table")
    pptsdm::fid_monitor(data = csv_data, station_type = "nedap", ...)
    pptsdm::station_monitor(data = csv_data, station_type = "nedap", ...)
    pptsdm::growth_monitor(data = csv_data, threshold = 1, ...)
  }
  
  # Save the arguments to a configuration file
  config_file <- file.path(short_temp_path, paste0("monitor_", taskname, ".txt"))
  cat("arg_list <- ", capture.output(dput(rscript_args)), file = config_file)
  
  write_function_to_script <- function(func, file_path, config_path) {
    func_name <- deparse(substitute(func))
    lines <- capture.output(dump(func_name, stdout()))
    lines <- c(lines, sprintf("source('%s')", config_path))
    lines <- c(lines, sprintf("do.call(%s, arg_list)", func_name))
    
    if (!file.exists(script_file)) {
      file.create(script_file)
    }
    
    con <- file(script_file, "w")
    on.exit(close(con), add = TRUE)
    writeLines(lines, con)
  }
  
  write_function_to_script(func = my_function, file_path = script_file, config_path = config_file)
  
  # Schedule the task
  taskscheduleR::taskscheduler_create(taskname = taskname,
                                      rscript = script_file, 
                                      schedule = schedule,
                                      starttime = starttime,
                                      startdate = startdate,
                                      rscript_args = NULL,
                                      ...)
}
```

```{r examples-monitor_schedule}
monitor_schedule(
  taskname = "ppt_csv_monitor",
  schedule = "DAILY",
  starttime = "10:05",
  startdate = format(Sys.Date(), "%Y/%m/%d"),
  rscript_args = list(csv_path = "C:/Users/Dell/Downloads/test",
                      save_path = "C:/Users/Dell/Downloads/test"))
```

That's it ! This the end of the documented story of our package. All components are there.

```{=html}
<!-- 
# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()` 
-->
```
```{r development-inflate, eval=FALSE}
# Execute in the console directly
fusen::inflate(flat_file = "dev/station_pig_monitor.Rmd", check = T, vignette_name = "Basic Usage")
```

```{=html}
<!-- 
- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory 
-->
```
