---
title: "flat_teaching.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{=html}
<!-- 
Run this 'development' chunk

Store every call to library() that you need to run chunks line by line, as in a classical Rmd for analysis
-->
```
```{r development, include=FALSE}
library(data.table)
library(ggplot2)
library(tidyfst)
library(robustbase)
library(taskscheduleR)
library(patchwork)
library(lubridate)
```

```{=html}
<!--
# Description of your package

This will fill the description of your package.
Fill and run the content of this chunk, before anything else. 

Note: when you will use other flat templates, this part will be in a separate file. Do not be surprised!
-->
```
```{r description, eval=FALSE}
# Describe your package
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "Breeding Tools",
    Description = "An R package that can monitor the csv data and stations from the Nedap in pig farm.",
     `Authors@R` = c(
      person("Guo Meng", email = "tony2015116@163.com", role = c("aut", "cre")),
      person(given = "Guo Meng", role = "cph")
    )
  ),
  overwrite=T
)
# Define License with use_*_license()
usethis::use_mit_license("Guo Meng")
```

# fid_monitor

You can use `fid_monitor()` to monitor the feed intake of each pig in the nedap or fire pig performance test station as well as the total feed intake of all pigs.

```{r function-fid_monitor}
#' Feed intake monitor of pig performance test station
#' 
#' @param data A data frame or data table containing the nedap or fire pig performance test data to be processed. Columns must include 'visit_time', 'location', 'responder', 'feed_intake'.
#' 
#' @param begin_date An optional Date object or character string specifying the beginning date for the data to be processed. If not provided, all dates in the data will be considered.
#' 
#' @param station_type A character string specifying the type of station. This must be either 'nedap' or 'fire'.
#' @param save_path A character string specifying the path where the output PDF will be saved.
#' 
#' @importFrom data.table ":="
#' @importFrom data.table ".SD"
#' 
#' @return This function does not return a value. It saves a PDF file to the specified path.
#' @export
#' 
fid_monitor <- function(data, begin_date=NULL, station_type, save_path) {
  if (missing(data)) stop("Please provide 'data' argument.")
  if (missing(station_type)) stop("Please provide 'station_type' argument.")
  if (missing(save_path)) stop("Please provide 'save_path' argument.")
  # Argument checks
  if (!is.data.frame(data) && !data.table::is.data.table(data)) {
    stop("The 'data' argument must be a data.frame or a data.table.")
  }
  
  if (!is.null(begin_date)) {
    if (!inherits(begin_date, "Date") && !is.character(begin_date)) {
      stop("Error: 'begin_date' argument must be a Date object or character string.")
    }
    
    if (is.character(begin_date)) {
      begin_date <- as.Date(begin_date)
    }
  }
  
  if (!is.character(station_type) || !(station_type %in% c("nedap", "fire"))) {
    stop("The 'station_type' argument must be either 'nedap' or 'fire'.")
  }
  
  if (!is.character(save_path) || !dir.exists(save_path)) {
    stop("The 'save_path' argument must be a valid directory path.")
  }
  
  visit_time <- . <- location <- responder <- feed_intake <- all_feed_a_station_one_day <- total_intake <- percent_intake <- Date <- Consumed <- total_intake <- percent_intake <- ndt <- plot1 <- plot2 <- NULL
  
  if (!data.table::is.data.table(data)) {
    data <- data.table::setDT(data)
  }
  prepare_nedap_data <- function(data, begin_date = NULL) {
    temp1 <- unique(data)[,`:=`(c("date", "time"),data.table::tstrsplit(visit_time," ", fixed = TRUE))][, `:=`(c("date"), lubridate::ymd(date))][,!c("visit_time", "time")]
    temp2 <- temp1[, keyby = .(location, responder, date),.(total_intake = round(sum(feed_intake) / 1000, digits = 4))][,`:=`(all_feed_a_station_one_day, sum(total_intake)), by = .(location, date)][, `:=`(percent_intake, total_intake / all_feed_a_station_one_day)]
    to_factor = c("location", "responder")
    temp2[, `:=`((to_factor), purrr::map(.SD, as.factor)), .SDcols = to_factor]
    if (!is.null(begin_date)) {
      temp2 <- temp2[date >= begin_date]
    }
    return(temp2)
  }
  
  prepare_fire_data <- function(data, begin_date = NULL) {
    temp1 <- unique(data)[,`:=`(Date, lubridate::ymd(Date))]
    data.table::setnames(temp1, 1:3, c("location", "responder","date"))
    temp2 <- temp1[, keyby = .(location, responder, date),.(total_intake = round(sum(Consumed), digits = 4))][,`:=`(all_feed_a_station_one_day, sum(total_intake)),by = .(location, date)][, `:=`(percent_intake, total_intake / all_feed_a_station_one_day)]
    to_factor = c("location", "responder")
    temp2[, `:=`((to_factor), purrr::map(.SD, as.factor)),.SDcols = to_factor]
    if (!is.null(begin_date)) {
      temp2 <- temp2[date >= begin_date]
    }
    return(temp2)
  }
  
  # Prepare data based on station_type
  if (station_type == "nedap") {
    prepared_data <- prepare_nedap_data(data, begin_date = begin_date)
  } else if (station_type == "fire") {
    prepared_data <- prepare_fire_data(data, begin_date = begin_date)
  } else {
    stop("Invalid station_type. Supported types are 'nedap' and 'fire'.")
  }
  
  # Create the plots
  colors = c("#a6cee3", "#1f78b4", "#b2df8a", "#33a02c", "#fb9a99", "#e31a1c", "#fdbf6f", "#ff7f00", "#cab2d6", "#6a3d9a", "#b15928", "#8dd3c7", "#d9d9d9", "#80b1d3", "#00AFBB", "#01665e", "#003c30", "blue", "pink", "yellow", "red", "green", "#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#00AFBB", "#E7B800", "#FC4E07", "#1B9E77", "#D95F02", "#7570B3", "#E7298A", "#66A61E", "#E6AB02", "#A6761D", "#666666", "purple")
  #colors = as.character(palette.colors(n = 36, "Polychrome 36"))
  
  create_plots <- function(data, ...) {
    data[, list(list(.SD)), by = location
    ][, `:=`("plot1", purrr::map2(.SD[[1]], location, ~ ggplot2::ggplot(
      data = .x,
      ggplot2::aes(y = percent_intake,
                   x = date, fill = responder)
    ) + ggplot2::theme_bw() +
      ggplot2::geom_col(
        width = 0.8,
        na.rm = F,
        show.legend = T
      ) +
      ggplot2::ggtitle(.y) + ggplot2::scale_y_continuous(
        labels = scales::percent,
        limits = c(0, 1),
        breaks = seq(0, 1, 0.1)
      ) + ggplot2::theme(
        plot.title = ggplot2::element_text(
          color = "black",
          hjust = 0.5,
          size = 20
        ),
        axis.title.x = ggplot2::element_blank(),
        axis.title.y = ggplot2::element_text(size = 15),
        axis.text.x = ggplot2::element_text(size = 8, angle = 270),
        axis.text.y = ggplot2::element_text(size = 8),
        legend.title = ggplot2::element_text(size = 8),
        legend.text = ggplot2::element_text(size = 8),
        legend.position = "top",
        legend.margin = ggplot2::margin(10, 10, 10, 10),  # Adjust the legend margin
        legend.box.margin = ggplot2::margin(0, 0, 30, 0)  # Extra space at the bottom for the legend
      ) +
      ggplot2::guides(
        shape = ggplot2::guide_legend(override.aes = list(size = 7)),
        color = ggplot2::guide_legend(override.aes = list(size = 7))
      ) +
      ggplot2::ggtitle(paste0("location:", .y)) + ggplot2::scale_x_date(
        date_breaks = "1 day",
        date_labels = "%m-%d",
        date_minor_breaks = "1 day"
      ) +
      ggplot2::scale_fill_manual(
        na.value = "black",
        values = colors
      ), ...)), .SDcols = "V1"
    ][, `:=`("plot2", purrr::map2(.SD[[1]], location, ~ ggplot2::ggplot(data = .x,
                                                                        ggplot2::aes(
                                                                          y = total_intake, x = date, fill = responder
                                                                        )) +
                                    ggplot2::theme_bw() + ggplot2::geom_col(
                                      width = 0.8,
                                      na.rm = F,
                                      show.legend = F
                                    ) + ggplot2::theme(
                                      plot.title = ggplot2::element_text(
                                        color = "black",
                                        hjust = 0.5,
                                        size = 20
                                      ),
                                      axis.title.x = ggplot2::element_text(size = 15),
                                      axis.title.y = ggplot2::element_text(size = 15),
                                      axis.text.x = ggplot2::element_text(size = 8, angle = 270),
                                      axis.text.y = ggplot2::element_text(size = 8),
                                      legend.position = "none"
                                    ) +
                                    ggplot2::guides(
                                      shape = ggplot2::guide_legend(override.aes = list(size = 7)),
                                      color = ggplot2::guide_legend(override.aes = list(size = 7))
                                    ) +
                                    ggplot2::scale_x_date(
                                      date_breaks = "1 day",
                                      date_labels = "%m-%d",
                                      date_minor_breaks = "1 day"
                                    ) + ggplot2::scale_fill_manual(
                                      na.value = "black",
                                      values = colors
                                    ), ...)), .SDcols = "V1"][]
  }
  
  # Combine and save the plots
  save_combined_plots <- function(path_out, ...) {
    temp_plot <- create_plots(data = prepared_data, value = colors)
    
    # Calculate the number of unique locations
    num_locations <- length(unique(temp_plot$location))
    
    # Calculate the date range
    date_range <- range(prepared_data$date)
    num_days <- as.numeric(difftime(date_range[2], date_range[1], units = "days")) + 1
    
    # Set the minimum days for width calculation to 30
    num_days_for_width <- max(num_days, 50)
    
    # Calculate the PDF dimensions based on the number of locations and date range
    width_per_day <- 0.3 # 0.5 cm per day, you can adjust this value based on your preferences
    pdf_width <- num_days_for_width * width_per_day * 2 # Adjust width according to the date range and number of columns
    
    height_per_location <- 30 # 30 cm per location, you can adjust this value based on your preferences
    pdf_height <- height_per_location * ceiling(num_locations / 2) # Adjust height according to the number of locations and number of rows
    
    temp4 <- temp_plot[, `:=`("finals", purrr::pmap(.(.SD[[1]], .SD[[2]]), function(x, y) patchwork::wrap_plots(x, y, ncol = 1))), .SDcols = c("plot1","plot2")][]
    temp5 <- patchwork::wrap_plots(temp4$finals, ncol = 2)
    
    ggplot2::ggsave(
      file.path(save_path, "feed_intake_monitor.pdf"),
      temp5,
      width = pdf_width,
      height = pdf_height,
      units = "cm",
      dpi = "retina",
      limitsize = FALSE,
      ...
    )
  }
  save_combined_plots(save_path)
}
```

```{r examples-fid_monitor}
data <- data.table::fread("C:/Users/Dell/Downloads/test/ppt_test_data.csv")
fid_monitor(data = data, station_type = "nedap", save_path = "C:/Users/Dell/Downloads/test")
```

```{=html}
<!-- 
This first section shows:

- the three parts necessary for a package: 'function', 'examples' and 'tests'.  
  + Note that the three following chunks have names accordingly.

-->
```
```{=html}
<!--
Here is an example on how to use the function.
This should be a reproducible and working example
-->
```
# station_monitor

You can use function of `station_monitor()` to monitor pig performance test data from nedap and fire pig performance test stations. This function can monitor the changes in the number of pigs, total visitation time of pigs, total number of visits, changes in total feed intake, and also monitor the changes in pig weights for a specific pig performance test station.

```{r function-station_monitor}
#' Feed intake monitor of pig performance test station
#' 
#' @param data A data frame or data table. This is the data to be processed. It should have specific columns depending on the station type.
#' @param begin_date An optional parameter. If provided, only data from this date onwards will be considered. It can be a Date object or a character string in the form 'yyyy-mm-dd'. Default is NULL, which means all dates in the data will be considered.
#' @param station_type A character string specifying the type of station. This must be either 'nedap' or 'fire'.
#' @param save_path A character string specifying the path where the output PNG files will be saved.
#' 
#' @importFrom data.table ":=" "CJ" ".SD"
#' 
#' @return This function does not return a value. It saves PNG files to the specified path.
#' @export
#' 
station_monitor <- function (data, begin_date=NULL, station_type, save_path)
{
  if (missing(data)) stop("Please provide 'data' argument.")
  if (missing(station_type)) stop("Please provide 'station_type' argument.")
  if (missing(save_path)) stop("Please provide 'save_path' argument.")
  # Argument checks
  if (!is.data.frame(data) && !data.table::is.data.table(data)) {
    stop("The 'data' argument must be a data.frame or a data.table.")
  }
  
  if (!is.null(begin_date)) {
    if (!inherits(begin_date, "Date") && !is.character(begin_date)) {
      stop("Error: 'begin_date' argument must be a Date object or character string.")
    }
    
    if (is.character(begin_date)) {
      begin_date <- as.Date(begin_date)
    }
  }
  
  if (!is.character(station_type) || !(station_type %in% c("nedap", "fire"))) {
    stop("The 'station_type' argument must be either 'nedap' or 'fire'.")
  }
  
  if (!is.character(save_path) || !dir.exists(save_path)) {
    stop("The 'save_path' argument must be a valid directory path.")
  }
  visit_time <-
    responder <-
    . <-
    location <-
    animal_number <-
    duration <-
    feed_intake <-
    Entry <-
    Exit <- Consumed <- weight <- ndt <- . <- items <- plot1 <- .N <- V1 <- hour <- plot_name <- NULL
  
  if (!data.table::is.data.table(data)) {
    data <- data.table::setDT(data)
  }
  # Prepare data based on station_type
  prepare_nedap_data <- function(data, begin_date = NULL) {
    temp1 <-
      unique(data)[, `:=`(c("date", "time"),data.table::tstrsplit(visit_time," ", fixed = TRUE))
      ][, `:=`(c("date"), data.table::as.IDate(date))
      ][,!c("visit_time", "time")]
    if (!is.null(begin_date)) {
      temp1 <- temp1[date >= begin_date]
    }
    temp2 <- unique(temp1, by = c("location", "responder", "date"))[!is.na(responder)
    ][, keyby = .(location,date), .(animal_number = .N)]
    temp3 <- temp1[!is.na(animal_number)
    ][, keyby = .(location,date), .(`total_intake_duration(min)` = round(sum(duration) / 60,digits = 4),total_intake = round(sum(feed_intake) / 1000,digits = 4),visit_number = .N)]
    temp5 <- merge(temp2, temp3, all.x = TRUE)
    list(temp5 = temp5, temp1 = temp1)
  }
  
  prepare_fire_data <- function(data, begin_date = NULL) {
    temp1 <- unique(data)[, `:=`(Entry,do.call(paste, c(.SD, sep = " "))), .SDcol = c("Date","Entry")
    ][, `:=`(Exit, do.call(paste, c(.SD, sep = " "))),.SDcol = c("Date", "Exit")
    ][, `:=`(c("Entry", "Exit"),lapply(.SD, lubridate::ymd_hms)), .SDcol = c("Entry","Exit")
    ][, `:=`(duration,data.table::fifelse(Exit -Entry < 0 & lubridate::hour(Exit) == 0,Exit - Entry + lubridate::ddays(1), Exit - Entry))]
    data.table::setnames(temp1,
                         c(1:3, 9),
                         c("location",
                           "responder", "date", "weight"))
    temp1 <- unique(temp1)[, `:=`(date, lubridate::ymd(date))]
    if (!is.null(begin_date)) {
      temp1 <- temp1[date >= begin_date]
    }
    temp2 <- unique(temp1, by = c("location", "responder","date"))[!is.na(responder)
    ][, keyby = .(location, date), .(animal_number = .N)]
    temp3 <- temp1[!is.na(responder)
    ][, `:=`(duration, as.numeric(duration))
    ][,keyby = .(location, date), .(`total_intake_duration(min)` = round(sum(duration) / 60,digits = 4), total_intake = round(sum(Consumed),digits = 4),visit_number = .N)]
    temp5 <- merge(temp2, temp3, all.x = TRUE)
    list(temp5 = temp5, temp1 = temp1)
  }
  
  
  # Prepare data based on station_type
  if (station_type == "nedap") {
    prepared_data_list <- prepare_nedap_data(data, begin_date = begin_date)
    prepared_data <- prepared_data_list$temp5
    temp1 <- prepared_data_list$temp1
  } else if (station_type == "fire") {
    prepared_data_list <- prepare_fire_data(data, begin_date = begin_date)
    prepared_data <- prepared_data_list$temp5
    temp1 <- prepared_data_list$temp1
  } else {
    stop("Invalid station_type. Supported types are 'nedap' and 'fire'.")
  }
  
  # The rest of the code remains the same.
  # 将第3到第6列的类型转换为numeric
  prepared_data[, (3:6) := lapply(.SD, as.numeric), .SDcols = 3:6]
  
  # 使用melt函数
  temp6 = data.table::melt(prepared_data,
                           id.vars = c("location", "date"),
                           measure.vars = 3:6,
                           variable.name = "items",
                           value.name = "values")
  
  temp6_2 <- temp1[!is.na(location), .(location, date, weight)
  ][, list(list(.SD)), by = location # nest by location
  ][, `:=`("V1", purrr::map(.SD[[1]], function(data) {data[data.table::CJ(date = tidyr::full_seq(date, 1)), on = .(date)
  ][data.table::CJ(date = date, unique = TRUE), on = .(date)]})), .SDcols = "V1"
  ][, `:=`("plot1", purrr::map2(.SD[[1]], location, ~ggplot2::ggplot(data = .x, ggplot2::aes(x = date, y = weight, group = date)) +
                                  ggplot2::geom_boxplot(outlier.color = "red") +
                                  ggplot2::scale_y_continuous(breaks = scales::pretty_breaks(n = 10)) +
                                  cowplot::background_grid(minor = "none") +
                                  ggplot2::scale_x_date(date_breaks = "1 day", date_labels = "%d") +
                                  ggplot2::theme_bw() +
                                  ggplot2::theme(legend.position = "none",
                                                 axis.title.x = ggplot2::element_blank(),
                                                 axis.text.x = ggplot2::element_text(angle = -90),
                                                 axis.text = ggplot2::element_text(size = 8)))), .SDcols = "V1"
  ][ , V1 := NULL
  ][]
  
  temp7 <- temp6[, list(list(.SD)), by = location
  ][, `:=`("V1", purrr::map(.SD[[1]], function(data) {data[CJ(date = tidyr::full_seq(date, 1)), on = .(date)
  ][CJ(date = date, items = items, unique = TRUE), on = .(date, items)
  ][!is.na(items)
  ][,`:=`(items, factor(items, labels = c("N", "visit_time/min","feed_intake/kg", "visit_number")))]})), .SDcols = "V1"
  ][, `:=`("plot2", purrr::map2(.SD[[1]], location,~ggplot2::ggplot(data = .x, ggplot2::aes(x = date, y = values)) +
                                  ggplot2::geom_point(ggplot2::aes(col = items)) +
                                  ggplot2::geom_line(ggplot2::aes(col = items)) +
                                  ggplot2::theme_bw() +
                                  ggplot2::facet_grid(items ~ ., scales = "free") +
                                  ggplot2::scale_x_date(date_breaks = "1 day", date_labels = "%m") +
                                  ggplot2::scale_colour_brewer(palette = "Set1") +
                                  ggplot2::theme(strip.text.y = ggplot2::element_text(angle = 0,hjust = 0),
                                                 legend.position = "none",
                                                 axis.title = ggplot2::element_blank(),
                                                 axis.text.x = ggplot2::element_text(angle = -90),
                                                 axis.text = ggplot2::element_text(size = 8),
                                                 strip.placement = "outside",
                                                 strip.background = ggplot2::element_rect(colour = "white", fill = "white")) +
                                  ggplot2::ggtitle(paste0("Location:", .y)) +
                                  cowplot::background_grid(minor = "none"))), .SDcols = "V1"][]
  
  temp8 <- merge(temp7, temp6_2, by = "location", all.x = TRUE)
  temp9 <- temp8[, `:=`("finals", purrr::pmap(.(.SD[[1]], .SD[[2]]), function(x, y) patchwork::wrap_plots(x, y, nrow = 2))), .SDcols = c("plot2","plot1")
  ][, plot_name := paste0(location, "_stations.png")][]
  
  # 根据天数计算图片的长度和宽度
  # 使用 map() 遍历 V1 列中的所有列表，计算唯一日期数
  days <- purrr::map_dbl(temp9$V1, ~ length(unique(.x$date)))
  height <- ifelse(days <= 7, 8, ifelse(days <= 14, 8, ifelse(days <= 30, 8, 8)))
  width <- ifelse(days <= 7, 5, ifelse(days <= 14, 10, ifelse(days <= 30, 13, 16)))
  
  purrr::walk2(
    temp9$plot_name,
    temp9$finals,
    ~ ggplot2::ggsave(
      filename = file.path(save_path, .x),
      plot = .y,
      height = height,
      width = width
    )
  )
}
```

```{r examples-station_monitor}
data <- data.table::fread("C:/Users/Dell/Downloads/test/ppt_test_data.csv")
station_monitor(data = data, station_type = "nedap", save_path = "C:/Users/Dell/Downloads/test")
```

# monitor_schedule

You can use `monitor_schedule` to set when to run the `fid_monitor()` and \`station_monitor()\`.

```{r function-monitor_schedule}
#' Feed intake monitor of pig performance test station
#' 
#' @param taskname A character string with the name of the task. Defaults to the filename. Should not contain any spaces
#' @param schedule Either one of 'ONCE', 'MONTHLY', 'WEEKLY', 'DAILY', 'HOURLY', 'MINUTE', 'ONLOGON', 'ONIDLE
#' @param starttime A timepoint in HH:mm format indicating when to run the script. Defaults to within 62 seconds
#' @param startdate A date that specifies the first date on which to run the task. Only applicable if schedule is of type 'MONTHLY', 'WEEKLY', 'DAILY', 'HOURLY', 'MINUTE'. Defaults to today in '%d/%m/%Y' format. Change to your locale format if needed
#' @param rscript_args Character string with further arguments passed on to Rscript
#' @param ... other parameters
#'
#' @importFrom utils "capture.output"
#'
#' @return pdf and pngs
#' @export
#' 
monitor_schedule <- function(taskname, schedule, starttime, startdate, rscript_args = NULL, ...) {
  if (missing(taskname) || !is.character(taskname) || length(taskname) != 1) {
    stop("taskname must be a single character string")
  }
  
  if (missing(schedule) || !is.character(schedule) || length(schedule) != 1) {
    stop("schedule must be a single character string")
  }
  
  if (missing(starttime) || !is.character(starttime) || length(starttime) != 1) {
    stop("starttime must be a single character string")
  }
  
  if (missing(startdate) || !is.character(startdate) || length(startdate) != 1) {
    stop("startdate must be a single character string")
  }
  
  if (missing(rscript_args) || !is.list(rscript_args)) {
    stop("rscript_args must be a list of arguments")
  }
  
  # Save the function to a temporary script file with a shorter path
  short_temp_path <- "C:/Temp"
  dir.create(short_temp_path, showWarnings = FALSE)
  script_file <- file.path(short_temp_path, paste0(taskname, "_", sample(letters, 1), ".R"))
  
  my_function <- function(csv_path, ...) {
    csv_files <- list.files(csv_path, full.names = T, pattern = ".csv", recursive = T)
    csv_data <- pptos::import_csv(csv_files, package = "data.table")
    pptsdm::fid_monitor(data = csv_data, station_type = "nedap", ...)
    pptsdm::station_monitor(data = csv_data, station_type = "nedap", ...)
  }
  
  # Save the arguments to a configuration file
  config_file <- file.path(short_temp_path, paste0("monitor_", taskname, ".txt"))
  cat("arg_list <- ", capture.output(dput(rscript_args)), file = config_file)
  
  write_function_to_script <- function(func, file_path, config_path) {
    func_name <- deparse(substitute(func))
    lines <- capture.output(dump(func_name, stdout()))
    lines <- c(lines, sprintf("source('%s')", config_path))
    lines <- c(lines, sprintf("do.call(%s, arg_list)", func_name))
    
    if (!file.exists(script_file)) {
      file.create(script_file)
    }
    
    con <- file(script_file, "w")
    on.exit(close(con), add = TRUE)
    writeLines(lines, con)
  }
  
  write_function_to_script(func = my_function, file_path = script_file, config_path = config_file)
  
  # Schedule the task
  taskscheduleR::taskscheduler_create(taskname = taskname,
                                      rscript = script_file, 
                                      schedule = schedule,
                                      starttime = starttime,
                                      startdate = startdate,
                                      rscript_args = NULL,
                                      ...)
}
```

```{r examples-monitor_schedule}
monitor_schedule(
  taskname = "ppt_csv_monitor",
  schedule = "DAILY",
  starttime = "10:05",
  startdate = format(Sys.Date(), "%Y/%m/%d"),
  rscript_args = list(begin_date = "2023-05-01", 
                      csv_path = "C:/Users/Dell/Downloads/test",
                      save_path = "C:/Users/Dell/Downloads/test"))
```

That's it ! This the end of the documented story of our package. All components are there.

```{=html}
<!-- 
# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()` 
-->
```
```{r development-inflate, eval=FALSE}
# Execute in the console directly
fusen::inflate(flat_file = "dev/station_pig_monitor.Rmd", check = T, vignette_name = "Basic Usage")
```

```{=html}
<!-- 
- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory 
-->
```
